\section*{Selected Peer-Reviewed Publications}

\subsection*{Published or In Press}

\subsubsection*{2022}

\noindent \textbf{Parks RM}, Benavides J, Anderson GB, Nethery RC, Navas-Acien A, Dominici F, Ezzati M, Kioumourtzoglou MA. (In Press). Title TBC. \textbf{Journal TBC}.

\subsubsection*{2021}

\noindent Nethery RC, Katz-Christy N, Kioumourtzoglou MA, \textbf{Parks RM}, Schumacher A, Anderson GB. (2021). Causal predictive models for forecasting health impacts of impending tropical cyclones, \textbf{Biostatistics} \href{https://academic.oup.com/biostatistics/advance-article/doi/10.1093/biostatistics/kxab047/6485226?guestAccessKey=378fb8f6-102d-4b21-a93d-b0a01353c19f#}{(link)} \medskip

\noindent Bock J, Srivastava P, Jessel S, Klopp JM, \textbf{Parks RM}. (2021). Heat vulnerability in New York City during COVID-19: A review of policies, tools and pilot survey results, \textbf{Journal of Extreme Events} \href{https://www.worldscientific.com/doi/10.1142/S2345737621500159}{(link)} \medskip

\noindent Kontis V, Bennett JE, \textbf{Parks RM}, Rashid T, Pearson-Stuttard J, Asaria P, Zhou B, Guillot M, Mathers CD, Khang Y, McKee M, Ezzati M. (2021). Lessons learned and lessons missed: Impact of the Covid-19 pandemic on all-cause mortality in 40 industrialised countries prior to mass vaccination, \textbf{Wellcome Open Research} \href{https://wellcomeopenresearch.org/articles/6-279/v1}{(link)} \medskip

\noindent Kruczkiewicz A, Klopp J, Fisher J, Mason S, McClain S, Sheekh NM, Moss R, \textbf{Parks RM}, Braneon C. (2021).\\Compound risks and complex emergencies require new approaches to preparedness, \textbf{PNAS} \href{https://www.pnas.org/content/118/19/e2106795118}{(link)} \medskip

\noindent Rowland S, \textbf{Parks RM}, Boehme AK, Goldsmith J, Rush J, Just AC, Kioumourtzoglou MA. (2021). The Association Between Ambient Temperature Variability and Myocardial Infarction: An Examination of Different Variability Metrics, \textbf{Environmental Research} \href{https://www.sciencedirect.com/science/article/pii/S0013935121005016}{(link)} \medskip

\noindent Elser H, \textbf{Parks RM}, Moghavem N, Bozinov B, Henderson VW, Rehkopf DH, Casey JA. (2021). Anomalously warm weather and acute care visits in patients with multiple sclerosis: A retrospective study of privately insured individuals in the U.S., \textbf{PLoS Medicine} \href{https://journals.plos.org/plosmedicine/article?id=10.1371/journal.pmed.1003580}{(link)} \medskip

\noindent \textbf{Parks RM}, Anderson GB, Nethery RC, Navas-Acien A, Dominici F, Kioumourtzoglou MA. (2021). Tropical cyclone exposure is associated with increased hospitalization rates in older adults, \textbf{Nature Communications} \href{https://www.nature.com/articles/s41467-021-21777-1}{(link)} \medskip

\noindent deSouza P, Braun D, \textbf{Parks RM}, Schwartz J, Dominici F, Kioumourtzoglou MA. (2021). Nationwide Study of Short-Term Exposure to Fine Particulate Matter and Cardiovascular Hospitalizations among Medicaid Enrollees, \textbf{Epidemiology} \href{https://journals.lww.com/epidem/Abstract/2021/01000/Nationwide_Study_of_Short_term_Exposure_to_Fine.2.aspx}{(link)}

\subsubsection*{2020}

\noindent Kontis V, Bennett JE, Rashid T, \textbf{Parks RM}, Pearson-Stuttard J, Guillot M, Asaria P, Zhou B, Battaglini M, Corsetti G, McKee M, Di Cesare M, Mathers C, Ezzati M. (2020). Magnitude, demographics and dynamics of the effect of the first wave of the COVID-19 pandemic on all-cause mortality in 21 industrialized countries, \textbf{Nature Medicine} \href{https://doi.org/10.1038/s41591-020-1112-0}{(link)} \medskip

\noindent \textbf{Parks RM}, Thalheimer L. (2020). The hidden burden of pandemics, climate change and migration on mental health, \textbf{UN International Organization for Migration (IOM) thematic series on health} \href{https://environmentalmigration.iom.int/blogs/hidden-burden-pandemics-climate-change-and-migration-mental-health}{(link)} \medskip

\noindent Kontis V, Bennett JE, \textbf{Parks RM}, Rashid T, Pearson-Stuttard J, Asaria P, Guillot M, Blangiardo M, Ezzati M. (2020). Age- and sex-specific total mortality impacts of the early weeks of the Covid-19 pandemic in England and Wales: Application of a Bayesian model ensemble to mortality statistics, \textbf{MedrXiv} \href{https://www.medrxiv.org/content/10.1101/2020.05.20.20107680v1}{(link)} \medskip

\noindent \textbf{Parks RM}, McLaren M, Rivett U, Thomson M. (2020). Vital signs: health security in South Africa. Chapter 5: climate, drought, food and health, \textbf{Brenthurst Foundation, Oppenheimer \& Sons} \href{http://www.thebrenthurstfoundation.org/article/vital-signs-health-security-in-south-africa/}{(link)} \medskip

\noindent \textbf{Parks RM}, Bennett JE, Tamura-Wicks H, Kontis V, Toumi R, Ezzati M. (2020). Anomalously warm temperatures are associated with increased injury deaths, \textbf{Nature Medicine} \href{https://www.nature.com/articles/s41591-019-0721-y}{(link)}
% (In the top 1\% of all research outputs scored by Altmetric)\\

\subsubsection*{2019}

\noindent Bennett JE*, Tamura-Wicks H*, \textbf{Parks RM}, Burnett RT, Pope CA III, Bechle MJ, Marshall JD, Danaei G, Ezzati M. (2019). National and county life expectancy loss associated with particulate matter pollution in the USA: a spatiotemporal analysis, \textbf{PLoS Medicine} \href{https://doi.org/10.1371/journal.pmed.1002856}{(link)} \medskip

\noindent \textbf{Parks RM}, McLaren M, Toumi R, Rivett U. (2019). Experiences and lessons in managing water from Cape Town, \textbf{Grantham Briefing Papers} \href{https://bit.ly/2Uu9oAh}{(link)}

\newpage

% HEADER 
\input{sections/header}

\section*{Selected Publications (Continued)}

\subsubsection*{2016 -- 2018}

\noindent \textbf{Parks RM}, Bennett JE, Foreman KJ, Toumi R, Ezzati M. (2018). National and regional seasonal dynamics of all-cause and cause-specific mortality in the USA from 1980 to 2016, \textbf{eLife}  \href{https://doi.org/10.7554/eLife.35500}{(link)} \medskip
% (In the top 5\% of all research outputs scored by Altmetric)\\

\noindent \textbf{Parks RM}. (2016). Weather, climate and health, \textbf{Weather} \href{https://doi.org/10.1002/wea.2752}{(link)} \medskip

\noindent * Contributed equally to this work

\begin{center} \line(1,0){450} \end{center}