\subsection*{Under Revision, Under Review, Submitted, or In Preparation}

\noindent \textbf{Parks RM}, Nunez Y, Balalian A,  Gibson EA, Hansen J, Raaschou-Nielsen O, Ketzel M, Khan J, Brandt J, Vermeulen R, Peters S, Goldsmith J, Re DB, Weisskopf MG, Kioumourtzoglou MA. (Under Revision). Long-term traffic-related air pollutant exposure and amyotrophic lateral sclerosis diagnosis in Denmark: A Bayesian hierarchical analysis. \medskip

\noindent Gibson EA, \textbf{Parks RM}, Paisley J, Goldsmith J, Factor-Litvak P, Herbstman JB, Kioumourtzoglou MA. (Under Revision). Prenatal endocrine disrupting chemical exposure \& child IQ: Accounting for uncertainty in pattern identification in a two-stage health analysis. \medskip

\noindent Nunez Y, Balalian A, \textbf{Parks RM}, He M, Hansen J, Raaschou-Nielsen O, Ketzel M, Khan J, Brandt J, Vermeulen R, Peters S, Goldsmith J, Re DB, Weisskopf MG, Kioumourtzoglou MA. (Submitted). Critical time windows in the association between PM2.5 exposure and amyotrophic lateral sclerosis: a case-control study in Denmark. \medskip

\noindent Elser H,* Rowland ST,* Tartof SY, \textbf{Parks RM}, Bruxvoort K, Morello-Frosch R, Robinson SC, Pressman A, Wei RX, Casey JA (Submitted). Ambient temperature and risk of urinary tract infection in California: A time-stratified case-crossover study using electronic health records. \medskip

\noindent \textbf{Parks RM}, Rowland ST, Do V, Boehme AK, Hart CL, Kioumourtzoglou MA. (In Preparation). Association of temperature and alcohol- and substance-related disorder hospitalizations in New York State: A distributed lag non-linear case-crossover analysis.

% \noindent \textbf{Parks RM}, Hardwick S, Sparks N \& Toumi R. Using IMAGE, a multi-site, multivariate stochastic weather generator, to model European heat waves under climate change\\

% \noindent Matthews-Trigg N, \textbf{Parks RM}, Jones H, Ebi K. \& Shumake-Guillemot J. Extreme heat intervention typology \& inventory: a literature review

% \noindent * Contributed equally to this work
											
\begin{center} \line(1,0){450} \end{center}